Paper_analyses

### 2022-02-10 Paper_Analyses_subj_obje_arousal1.Rmd
finished boorstrap and resampling tests

# 
# quanti

@@

eigen_first%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
  ggplot(aes(eigenvalue))+
  geom_histogram(alpha = .2)+
    geom_density()+
  # facet_grid(~component)+
    geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
  geom_point(x = res.mfa_bio_vs_self2_k2$eig[1],y = 10,size = 2, color = "red")+

  theme_classic()+
  geom_vline(xintercept = 1, linetype = "dashed")+
  ggtitle("distribution of boostraped eigen values for component  1 
          red dot = observed eigenvalue, boostrapped 95%CI")+
  annotate("text", x = 1.2, y = 20, label = "prob of obs eigen>= boot eigen = 51%")

table(eigen_first$eigenvalue>1)

t.testsample1<- eigen_first%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 1" )

t.test(1.14, mu = mean(t.testsample1$eigenvalue))

# boostrap ratio
# proposed by abdi for factir scores
mean(t.testsample1$eigenvalue, na.rm = TRUE)/(sd(t.testsample1$eigenvalue,na.rm = TRUE))

```{r}
# check eigen vectors (correlations

# checpartials_first_n40_withrepl

# check groups

# binom.test(eigen_first$eigenvalue>1)

@@

```
  # geom_vline(xintercept = 1, linetype = "dashed")

table(eigen_first$eigenvalue>1)

# boot::boot()

t.test_sample<- eigen_first%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
  mutate(eigen_d = (mean(eigenvalue))- res.mfa_bio_vs_self2_k2$eig[1])%>%
   mutate(eigen_d2 = eigenvalue- res.mfa_bio_vs_self2_k2$eig[1])
t.test(t.test_sample$eigen_d2)

# technially a t test is calculated as the differnce between current mean and pipulation mean devied by population variance, since we often don't have population variance we estimate it from the sample

# will this give us a t?
(res.mfa_bio_vs_self2_k2$eig[1]- (mean(t.test_sample$eigenvalue, na.rm = TRUE)))/ 
  (sd(t.test_sample$eigenvalue))

mean(t.test_sample$eigen_d2)/  (sd(t.test_sample$eigenvalue))

resamp_1st%>%
  subset(sim_no = 1)%>%
  subset(is.na(ssid) == FALSE)%>%
  subset(ssid ==  306)

?fabricatr::fabricate()

# ),
  # pollution = rnorm(N, mean = 5))
fabricatr::fabricate(
  stim = add_level(N = 3),
  id = add_level(N = 30),
  Var1 = runif(N, 2, 10),
  Var2 = runif(N, -5, 6),
  Var2 = runif(N, .2, 2),
  Var4 = runif(N, -10, 10),
  Var5 = runif(N, -10, 10)
))%>%
  arrange(stim)

fabricate(
  primary_schools = add_level(N = 3, 
                              var1 = runif(N, 0, 10)),
  students = link_levels(N = 30,
                          by=join(var1, rho = 0.5)))

# dimension 2

quantile(eigen_first$eigenvalue,.95, na.rm = TRUE)
eigen_first%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>%
    subset(!is.na(eigenvalue) & component == "comp 2" )%>%
  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE),
         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE))%>%
  ggplot(aes(eigenvalue))+
  geom_histogram(alpha = .2)+
    geom_density()+
   geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
  geom_point(x = res.mfa_bio_vs_self2_k2$eig[2],y = 10,size = 2, color = "red")+
  # geom_vline(aes(xintercept = perc_95), linetype = "dotted")+
  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y = 10))+
  theme_classic()

  # first dimension is significant

 # same thing as above with variance
# quantile(eigen_first$`percentage of variance`,.95, na.rm = TRUE)
eigen_first%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>%
  subset(!is.na(`percentage of variance`) & component == "comp 1" )%>%
  mutate(perc_5 = quantile(`percentage of variance`,.025, na.rm = TRUE),
         perc_95 = quantile(`percentage of variance`,.975, na.rm = TRUE))%>%
  ggplot(aes(`percentage of variance`))+
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y = .3), color = "gray30")+
  geom_point(x = res.mfa_bio_vs_self2_k2$eig[1,2],y = .3,size = 3, color = "red")+

    # geom_vline(aes(xintercept = perc_5), linetype = "dotted")+
  # geom_vline(aes(xintercept = perc_95), linetype = "dotted")+
  theme_classic()

@@

cor_first %>%
  mutate(variable = as.factor(substr(rownames(cor_first), 1,6)))%>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable
  group_by(variable)%>%
   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  # subset(variable == "arousa"|variable == "valenc")%>%
  # select(c("arousal", "valence"))%>%
  ggplot(aes(Dim.1)) +
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
  facet_grid(~variable)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  #  geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()

cor_first %>%
  mutate(variable = as.factor(substr(rownames(cor_first), 1,6)))%>%
    subset(!is.na(Dim.2)) %>%
  # create interval per variable
  group_by(variable)%>%
   mutate(perc_5 = quantile(Dim.2,.025, na.rm = TRUE),
         perc_95 = quantile(Dim.2,.975, na.rm = TRUE))%>%
  # subset(variable == "arousa"|variable == "valenc")%>%
  # select(c("arousal", "valence"))%>%
  ggplot(aes(Dim.2)) +
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
  facet_grid(~variable)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
   geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()

@@

partials_first%>%
  mutate(dimension = as.factor(substr(rownames(partials_first), 1,4)),
         group = as.factor(substr(rownames(partials_first), 5,9)))%>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable
  group_by(dimension, group)%>%
   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  ggplot(aes(Dim.1)) +
  geom_histogram(bins = 500)+
  # geom_histogram(aes(y=..density..), alpha=0.5,
  #                position="identity")+
  geom_density(alpha=.2) +
   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =10 ), color = "gray30")+
  facet_grid(dimension~group)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()
  ylim(0,100)

@@

# we sgoudl probably store cos2 rather than correlatiopn
# their cos2 values corresponding to their quality of representation on the factor map
groups_first%>%
  mutate(group = as.factor(substr(rownames(groups_first), 1,4)))%>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable

  gather(dimension, value_dimenion, -group, -sim_no) %>%
  # -perc_5,-perc_95, 
   group_by(group,dimension)%>%
   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))%>%

  ggplot(aes(value_dimenion, color = group)) +
  geom_histogram(bins = 500)+
  # geom_histogram(aes(y=..density..), alpha=0.5,
  #                position="identity")+
  geom_density(alpha=.2) +
   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =10 ), color = "gray30")+
  facet_grid(dimension~group)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()
  ylim(0,100)

@@

res.mfa_bio_vs_self2_scale
fviz_mfa_var(res.mfa_bio_vs_self2_scale, 
             "quanti.var", 
             palette = "jco", 
             col.var.sup = "violet", 
             repel = TRUE,
              addEllipses = TRUE,
             legend = "bottom",
              gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             col.var = "contrib" )

@@

clustering_new_pre_PCA3.1_copy<- clustering_new_pre_PCA3.1
colnames(clustering_new_pre_PCA3.1)

?sample

# this is slow so need to figure  a better way to to this but for now
clustering_new_pre_PCA3.1_copy %>%
  subset(ssid == 304 &val_cut_iaps == "mid" & aro_cut_iaps == "low" )%>%
  group_by(ssid)%>%
  transform(pup_basCor = sample(pup_basCor, replace = TRUE),
            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = TRUE),
            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = TRUE),
            arousal = sample(arousal, replace = F),
            valence = sample(valence, replace = F))

colnames(resampled_temp_reshuf)
 # create emopty dataframe
resamp_1st_reshuf<- data.frame(matrix(NA, nrow = 1, ncol = 9))
cnames_resamp_reshufl<- names(resampled_temp_reshuf)

colnames(resamp_1st_reshuf)<- cnames_resamp_reshufl
colnames(resamp_1st_reshuf)
# create emoty  storage rame for eigenvakues
eigen_first_reshuf<- as.data.frame(eugentest)
eigen_first_reshuf[,]<- NA

# eigen_first_reshuf<- as.data.frame(eigen_first_reshuf)

# create empty storage for correlations
cor_first_reshuf<- as.data.frame(cortest)
cor_first_reshuf[,]<- NA
# cor_first_reshuf<- as.data.frame(cor_first_reshuf)

# res.mfa_bio_vs_self2_k2$group$correlation
partials_first_reshuf <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
partials_first_reshuf[,]<- NA
partials_first_reshuf
partials_first_reshuf$sim_no<- NA

groups_first_reshuf<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
# res.mfa_bio_vs_self2_k2$group$correlation

groups_first_reshuf[,]<- NA
groups_first_reshuf
groups_first_reshuf$sim_no<- NA

for (i in 1:10000) {
  message(sprintf("$$$$$RUNING sim %i", i))

# changed below to replace treue - shuflle with replacement
  # https://stats.stackexchange.com/questions/104040/resampling-simulation-methods-monte-carlo-bootstrapping-jackknifing-cross?rq=1
  # See the question on permutation vs bootstrapping - "The permutation test is best for testing hypotheses and bootstrapping is best for estimating confidence intervals".
resampled_temp_reshuf <-    clustering_new_pre_PCA3.1_copy[,c(1,2,3, 5:9)] %>%
  group_by(ssid)%>%
  transform(pup_basCor = 
              sample(pup_basCor, replace = TRUE),
            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = TRUE),
            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = TRUE),
            arousal = sample(arousal, replace = TRUE),
            valence = sample(valence, replace = TRUE))

  resampled_temp_reshuf$sim_no = i
  # resampled_temp_reshuf$ssid_new <- as.factor(substr(resampled_temp_reshuf$stimDescription_unique,1,6))
  # resampled_temp_reshuf$newstim <- substr(resampled_temp_reshuf$stimDescription_unique,7,30)
  # resampled_temp_reshuf$stimDescription<- as.factor(resampled_temp_reshuf$stimDescription)

# run PCA on the resampled data
# ?list
    message(sprintf("$$$$$fitting PCA %i", i))
    mfa.res_reshuf <- FactoMineR::MFA(resampled_temp_reshuf[,c(1:8)], 
               group = c(3, 3, 2), 
               type = c("n", "s", "s"),
              # ind.sup = c(1),
              ncp = 2,
               name.group = c("pp_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = FALSE)

# store the eigen values
message(sprintf("$$$$$storing PCA %i", i))
eugentest_reshufl<- as.data.frame(mfa.res_reshuf$eig[1:2,])
eugentest_reshufl$sim_no<- i

cortest_reshufl<- as.data.frame(mfa.res_reshuf$quanti.var$cor)
cortest_reshufl$sim_no = i

partials_temp_reshuf<- as.data.frame(mfa.res_reshuf$partial.axes$cor)
partials_temp_reshuf$sim_no = i

# groups
group_temp_reshuf<- as.data.frame(mfa.res_reshuf$group$cos2)
group_temp_reshuf$sim_no = i

# update the initial d=frames
  message(sprintf("$$$$$upating dataframes %i", i))
  resamp_1st_reshuf<- (bind_rows(resamp_1st_reshuf, resampled_temp_reshuf))
eigen_first_reshuf<- bind_rows(eigen_first_reshuf, eugentest_reshufl)
cor_first_reshuf<- bind_rows(cor_first_reshuf, cortest_reshufl)
partials_first_reshuf<- bind_rows(partials_first_reshuf, partials_temp_reshuf)
groups_first_reshuf<- bind_rows(groups_first_reshuf, group_temp_reshuf)
  message(sprintf("$$$$$completed iteration%i", i))
}

eigen_first_reshuf%>%
  mutate(component =as.factor(substr(rownames(eigen_first_reshuf), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
  ggplot(aes(eigenvalue))+
  geom_histogram(bins = 500, alpha = .2)+
    geom_density(alpha = .3)+
  # facet_grid(~component)+
    # geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
  geom_point(x = res.mfa_bio_vs_self2_k2$eig[1],y = 10,size = 2, color = "red")+

  theme_classic()+
  geom_vline(aes(xintercept = perc_5, linetype = "dashed"))+
  geom_vline(aes(xintercept = perc_95, linetype = "dashed"))+
  ggtitle("distribution of boostraped eigen values for component  1 
          red dot = observed eigenvalue, boostrapped 95%CI")+
  annotate("text", x = 1.2, y = 20, label = "prob of obs eigen>= boot eigen = 51%")+
  ylim(0,10)

table(eigen_first$eigenvalue>1)

t.testsample1_reshudle<- eigen_first_reshuf%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 1" )

t.testsample1_reshudle$eigen_extreme <- t.testsample1_reshudle$eigenvalue>= res.mfa_bio_vs_self2_k2$eig[1]
table(t.testsample1_reshudle$eigen_extreme)

?binom.test
binom.test(c(0,1000))

# let's do component 2

t.testsample1_reshudledim2<- eigen_first_reshuf%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 2" )

t.testsample1_reshudledim2$eigen_extreme <- t.testsample1_reshudledim2$eigenvalue>= res.mfa_bio_vs_self2_k2$eig[2]
table(t.testsample1_reshudle$eigen_extreme)

eigen_first_reshuf%>%
  mutate(component =as.factor(substr(rownames(eigen_first_reshuf), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 2" )%>% #select only component 1 and remove nas I introduced in the dataframe
  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
  ggplot(aes(eigenvalue))+
  geom_histogram(bins = 500, alpha = .2)+
    geom_density(alpha = .3)+
  # facet_grid(~component)+
    # geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
  geom_point(x = res.mfa_bio_vs_self2_k2$eig[2],y = 10,size = 2, color = "red")+

  theme_classic()+
  geom_vline(aes(xintercept = perc_5, linetype = "dashed"))+
  geom_vline(aes(xintercept = perc_95, linetype = "dashed"))
  # ggtitle("distribution of boostraped eigen values for component  1 
  #         red dot = observed eigenvalue, boostrapped 95%CI")+
  # annotate("text", x = 1.2, y = 20, label = "prob of obs eigen>= boot eigen = 51%")
  # ylim(0,10)

```
cor reshudl

```{r}
cor_first_reshuf %>%
  mutate(variable = as.factor(substr(rownames(cor_first_reshuf), 1,6)))%>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable
  group_by(variable)%>%
   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  # subset(variable == "arousa"|variable == "valenc")%>%
  # select(c("arousal", "valence"))%>%
  ggplot(aes(Dim.1)) +
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
  facet_grid(~variable)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  #  geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()

cor_first_reshuf %>%
  mutate(variable = as.factor(substr(rownames(cor_first_reshuf), 1,6)))%>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable
  group_by(variable)%>%
   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  subset(variable == "valenc")%>%
  mutate(valenc_cor_extreme_d1 = Dim.1>= abs(mfa.res_reshuf$quanti.var$cor[5,1]),
         valenc_cor_extreme_d2 = Dim.2>= abs(mfa.res_reshuf$quanti.var$cor[5,2]))%>%
  mutate(prob_extree_vl_d1 = (sum(valenc_cor_extreme_d1)/n()),
         prob_extree_val_d2 = (sum(valenc_cor_extreme_d2)/n()))
# p 0.019	0.532

cor_first_reshuf %>%
  mutate(variable = as.factor(substr(rownames(cor_first_reshuf), 1,6)))%>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable
  group_by(variable)%>%
   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  subset(variable == "arousa")%>%
  mutate(arous_cor_extreme_d1 = Dim.1>= abs(mfa.res_reshuf$quanti.var$cor[4,1]),
         arous_cor_extreme_d2 = Dim.2>= abs(mfa.res_reshuf$quanti.var$cor[4,2]))%>%
  mutate(prob_extree_vl_d1 = (sum(arous_cor_extreme_d1)/n()),
         prob_extree_val_d2 = (sum(arous_cor_extreme_d2)/n()))
#  p 0.532; 0.019

cor_first_reshuf %>%
  mutate(variable = as.factor(substr(rownames(cor_first_reshuf), 1,6)))%>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable
  group_by(variable)%>%
   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  subset(variable == "pup_ba")%>%
  mutate(pup_cor_extreme_d1 = Dim.1>= abs(mfa.res_reshuf$quanti.var$cor[1,1]),
         pup_cor_extreme_d2 = Dim.2>= abs(mfa.res_reshuf$quanti.var$cor[1,2]))%>%
  mutate(prob_extree_puup_d1 = (sum(pup_cor_extreme_d1))/n(),
         prob_extree_puup_d2 = (sum(pup_cor_extreme_d2))/n())

```
# not significant

# scr

>>>>

```{r}
# quanti

@@

eigen_first%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
   # gather(dimension, value_dimenion, -group, -sim_no) %>%
  group_by(component)%>%
  # subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE))%>%
  ungroup()%>%
  mutate(eig_obs_dim = if_else(component == "comp 1", 
                               res.mfa_bio_vs_self2_k2$eig[1],
                               res.mfa_bio_vs_self2_k2$eig[2])) %>% #create 95% to descrive interval around the observed estimate
  # also store observed eige for each dimensions
  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
  ggplot(aes(eigenvalue))+
  geom_histogram(aes(y=..density..), alpha = .3) +  # scale histogram y
  geom_density(col = "red", alpha = .001)+
  # facet_grid(~component)+
  geom_errorbar(aes(xmin = perc_5, xmax=perc_95, y = 1), color = "gray30")+
  geom_point(aes(x = eig_obs_dim, y = 1),size = 2, color = "red", alpha = .3)+

  theme_classic()+
  geom_vline(aes(xintercept = perc_5), linetype = "dashed")+
    geom_vline(aes(xintercept = perc_95), linetype = "dashed")+

  geom_hline(yintercept = 0, linetype = "dashed")+
  facet_grid(~component)+
  ggtitle("distribution of boostraped eigen values for components 
          red dot = observed eigenvalue, boostrapped 95%CI")
  # annotate("text", x = 1.2, y = 20, label = "prob of obs eigen>= boot eigen = 51%")

use this in the resampling bit
```{r}

@@

 # same thing as above with variance
# quantile(eigen_first$`percentage of variance`,.95, na.rm = TRUE)

eigen_first %>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
  # gather(dimension, value_dimenion, -group, -sim_no) %>%
  group_by(component)%>%
  # subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
  mutate(perc_5 = quantile(`percentage of variance`,.025, na.rm = TRUE), 
         perc_95 = quantile(`percentage of variance`,.975, na.rm = TRUE))%>%
  ungroup()%>%
  mutate(perc_obs_dim = if_else(component == "comp 1", 
                               res.mfa_bio_vs_self2_k2$eig[1,2],
                               res.mfa_bio_vs_self2_k2$eig[2,2])) %>% #
  ggplot(aes(`percentage of variance`))+
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y = .3), color = "gray30")+
  geom_point(aes(x = perc_obs_dim,y = .3),size = 3, color = "red")+
  facet_grid(~component)+

    geom_vline(aes(xintercept = perc_5), linetype = "dotted")+
  geom_vline(aes(xintercept = perc_95), linetype = "dotted")+
  theme_classic()

@@

cor.test_obsmfa<- as.data.frame(res.mfa_bio_vs_self2_k2$quanti.var$cor) %>%
   mutate(variable = as.factor(substr(rownames(as.data.frame(res.mfa_bio_vs_self2_k2$quanti.var$cor)), 1,6)))%>%
 gather(dimension, value_dimenion, -variable)

cor_first1<- cor_first %>%
  mutate(variable = as.factor(substr(rownames(cor_first), 1,6)))%>%
    gather(dimension, value_dimenion, -variable, -sim_no) %>%
  group_by(variable,dimension)%>%
   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))

left_join(cor_first1, cor.test_obsmfa, by = c("variable", "dimension")) %>%
  ggplot(aes(value_dimenion.x)) +
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-2 ), color = "gray30")+
  facet_grid(~dimension)+
  geom_point(aes(x = value_dimenion.y, y = -2))+
    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+
  facet_grid(variable~dimension)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+

@@

res.mfa_bio_vs_self2_k2$partial.axes$cor

partials_first_1_obs<- as.data.frame(res.mfa_bio_vs_self2_k2$partial.axes$cor) %>%
   mutate(dimension_partial = as.factor(substr(rownames(as.data.frame(res.mfa_bio_vs_self2_k2$partial.axes$cor)), 1,4)),
           group = as.factor(substr(rownames(as.data.frame(res.mfa_bio_vs_self2_k2$partial.axes$cor)), 5,9)))%>%
 gather(dimension, value_dimenion,-group,-dimension_partial)

partials_first_1boot<- partials_first%>%
  mutate(dimension_partial = as.factor(substr(rownames(partials_first), 1,4)),
         group = as.factor(substr(rownames(partials_first), 5,9)))%>%
   gather(dimension, value_dimenion, -group, -sim_no, -dimension_partial) %>%
   group_by(dimension_partial,dimension,group)%>%
   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))

left_join(partials_first_1boot,partials_first_1_obs,by = c("dimension_partial", "group", "dimension")) %>%
  group_by(dimension_partial,dimension, group)%>%
  subset(dimension_partial == "Dim1")%>%
   # mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
   #       perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  ggplot(aes(value_dimenion.x)) +
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-5 ), color = "gray30")+
  geom_point(aes(x = value_dimenion.y, y = -5))+
    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+

  facet_grid(dimension~group)+

  geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .5)+
  theme_classic()+
  ggtitle("partial to dimension 1")

left_join(partials_first_1boot,partials_first_1_obs,by = c("dimension_partial", "group", "dimension")) %>%
  group_by(dimension_partial,dimension, group)%>%
  subset(dimension_partial == "Dim2")%>%
   # mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
   #       perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  ggplot(aes(value_dimenion.x)) +
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-5 ), color = "gray30")+
  geom_point(aes(x = value_dimenion.y, y = -5))+
    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+

  facet_grid(dimension~group)+

  geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .5)+
  theme_classic()+
  ggtitle("partial to dimension 2")

@@

groups_first_obs<- as.data.frame(res.mfa_bio_vs_self2_k2$group$correlation) %>%
   mutate(group = as.factor(substr(rownames(as.data.frame(res.mfa_bio_vs_self2_k2$group$correlation)), 1,4)))%>%
 gather(dimension, value_dimenion_obs,-group)

# we sgoudl probably store cos2 rather than correlatiopn
# their cos2 values corresponding to their quality of representation on the factor map
groups_first_1boot<- groups_first%>%
  mutate(group = as.factor(substr(rownames(groups_first), 1,4)))%>%
  gather(dimension, value_dimenion,-group,-sim_no)%>%
  # -perc_5,-perc_95, 
   group_by(group,dimension)%>%
   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))

?boot::boot.ci
boot::boot.ci(groups_first_1boot$value_dimenion, type = "bca")[1]
?bootBCa
bootBCa(.5, groups_first_1boot$value_dimenion, n = 2600)[1]
left_join(groups_first_1boot, groups_first_obs,by = c("group", "dimension"))%>%

  ggplot(aes(value_dimenion)) +
   geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +

   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-3 ), color = "gray30")+
   geom_point(aes(x = value_dimenion_obs, y = -3))+
    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+

  facet_grid(dimension~group)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()

  # bootsrap confidence intervals don't include point estimate
# seems like a consequnce of resampling a biased statistocs
# https://stats.stackexchange.com/questions/388931/bootstrap-confidence-intervals-do-not-include-the-observed-mean-can-this-be

# try plooting with corrected bca
# ?bca
# groups_first_1boot_CIcorrected<- groups_first%>%
#   mutate(group = as.factor(substr(rownames(groups_first), 1,4)))%>%
#   gather(dimension, value_dimenion,-group,-sim_no)%>%
#   # -perc_5,-perc_95, 
#    group_by(group,dimension)%>%
#   subset(!is.na(value_dimenion))%>%
#    mutate(perc_5 = bca(value_dimenion)[1],
#          perc_95 = bca(value_dimenion)[2])

groups_first_1boot_CIcorrected2<- groups_first%>%
  mutate(group = as.factor(substr(rownames(groups_first), 1,4)))%>%
  gather(dimension, value_dimenion,-group,-sim_no)

left_join(groups_first_1boot_CIcorrected2, groups_first_obs,by = c("group", "dimension"))%>%
  subset(!is.na(value_dimenion))%>%
  group_by(dimension,group)%>%
   mutate(perc_5 = bootBCa(mean(value_dimenion_obs), value_dimenion, n = 2600)[1],
         perc_95 = bootBCa(mean(value_dimenion_obs), value_dimenion, n = 2600)[2])%>%
   ggplot(aes(value_dimenion)) +
   geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +

   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-3 ), color = "gray30")+
   geom_point(aes(x = value_dimenion_obs, y = -3))+
    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+

  facet_grid(dimension~group)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()

```{r}
install.packages("coxed")
library(coxed)

bcatest<- partials_first_1boot%>%
  subset(!is.na(value_dimenion))

bcatest<- !is.na(bcatest)

bca(bcatest$value_dimenion)[1]

@@

res.mfa_bio_vs_self2_scale
fviz_mfa_var(res.mfa_bio_vs_self2_scale, 
             # "quanti.var", 
             palette = "jco", 
             col.var.sup = "violet", 
             repel = TRUE,
              addEllipses = TRUE,
             legend = "bottom",
              gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             col.var = "contrib" )

@@

to see the reshufllfing for the hierarqucal data see separate script - paper_analyses_subj1

# agg by pp
